---
title: "Shiny"
author: "Antonio Cesar Vergani Jr"
date: "Jan 2017"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## mtcars dataset

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models). This data is pre-loaded during the R installation.

## Summary of mtcars dataset

```{r mtcars, echo = TRUE}
summary(mtcars)
```

## Shiny app select cars based on the filters:

- Miles Per Gallon
- Number of cylinders
- Displacement
- Horse Power
- Transmission


## Links and References

The app developed for the first part of the assignment is avalilable at: https://verganijr.shinyapps.io/ShinyApp/

The presentation is available at: http://verganijr.github.io/Shiny

Code Files are avalilable on the GitHub: https://github.com/verganijr/Shiny

